How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-07-08 paper.tex
a bit more text

For this reason, asking the developers for help shouldn't be the \emph{first}
thing you do. Especially for software with a large community, chances are
someone else has run into similar difficulties, and you can probably save
yourself and the developers a lot of time if you look for solutions on your own
first. Indeed, quickly debugging your use of others' software is one of the
major skills one develops when learning to do computational research.

The first step is to check the manual. This might seem trivially obvious, but you'd be astonished how many emails developers get that are directly answered in the manual.

This might be an actual standalone
manual, or part of the web page for the software package, but if it exists it
should be your first stop. Look for a frequently asked questions list on the web site,

Search the internet for the error message (this works very well for software with thousands of users, less well with smaller packages)

>>>>

For this reason, asking the developers for help shouldn't be the \emph{first}
thing you do. Especially for software with a large community, chances are
someone else has run into similar difficulties, and you can probably save
yourself and the developers a lot of time if you look for solutions on your own
first. Indeed, quickly debugging your use of other people's software is one of
the major skills one develops when learning to do computational research.

The first step is to read the error message carefully, if there is one; this
obviously doesn't apply in all cases, but it's often applicable and far too
often skipped. It's true that many software packages have cryptic unhelpful
error messages, but far too often people write for help when the solution is
right in front of them. If the error message says ``Could not open file
foo.dat'', it's worth checking whether there is a file called ``foo.dat'' and if
not figuring out what was supposed to create it.

The second step is to check the manual. This might seem trivially obvious, but
you'd be astonished how many emails developers get that are directly answered in
the manual. If the manual is short, you can read the whole thing. If it's
longer, search for relevant-seeming keywords, scan the sections that seem to
pertain to your error message. If there's an FAQ (frequently asked questions)
list, check that first.

Next, search the internet for the error message; this works very well for
software with thousands of users, where it might very well deserve to be the
first option. It is less effective with less common packages, but it's an easy
thing to check, so you'd be foolish to skip it.

Finally, you can consider diving into the code. This decision depends very much
on the complexity of the package, your skill level, and how urgently you need
the solution. More often than not, comprehending the whole software package will
be too time consuming, but there are tricks and shortcuts one can use to at
least figure out where things might be going wrong. Figuring out where the error
is occurring can sometimes help you figure out why it happened, so examine the
stack trace if there is one. Alternatively, you can search the code base for the
error message, to see what drove the error; it's not uncommon for the comments
in the code to be clearer and more indicative of what could go wrong than the
error message itself. To be clear: as an end user, \emph{you are not obligated
to check the code}, but it can sometimes be a good shortcut to help you either
solve your problem on your own or give the developers what they need to solve
it.
